---
title: "Pixar Movies - Tidy Tuesday 1"
author: "Olivia Rosenthal"
format: html
execute: 
  warning: false
  message: false
---

## Intro
Everyone loves a good Pixar movie. You go as a kid, you go as a parent, you go as a college student who misses the innocence and nostalgia that Pixar movies inspire. But why does it feel like every movie is so darn long these days? Let's explore that through a plot. 

```{r}
#| echo: false
library(tidyverse)
library(openintro)
pixar_films <- read_csv(
  "https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-03-11/pixar_films.csv"
)

public_response <- read_csv(
  "https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-03-11/public_response.csv"
)
```

```{r}
pixar_data <- pixar_films |>
  left_join(public_response, by = "film")

```

```{r}
ggplot(pixar_data, aes(x = release_date, y = run_time))+
  geom_point()+
  labs(x = "Release Date", y="Run Time min", title = "Pixar Films Release Date and Run Times")
```

### Data Source

Data for this visualization was accessed through the 
[TidyTuesday Pixar Films dataset](https://github.com/rfordatascience/tidytuesday/tree/main/data/2025/2025-03-11).

**Original data:**  
Leung, Eric. *pixarfilms: An R Data Package to Explore Pixar Films, the People, and Reception Data*. 
Data provided mostly in part by Wikipedia.