---
title: "Taylor Swift - Tidy Tuesday 2"
author: "Olivia Rosenthal"
format: html
execute: 
  warning: false
  message: false
---
## Intro
The world has grown up along side Taylor Swift, and with that, her music has changed. Here is a visualization of her songs relationship to loudness and danceability. Each point represents a song and each color represents one of her albums. This data set was made in 2023 so it includes her songs and albums up to that date.

```{r}
#| echo: false
library(tidyverse)
library(openintro)
library(taylor)
Taylor_Swift <- read_csv(
  "https://raw.githubusercontent.com/rfordatascience/tidytuesday/refs/heads/main/data/2023/2023-10-17/taylor_album_songs.csv"
)
```

```{r}
ggplot(Taylor_Swift, aes(x = loudness, y = danceability, color = album_name))+
  geom_point()+
  scale_color_taylor_d() +
  labs(x = "Loudness", y="Danceability", title = "Taylor Swift Danceability", color = "Album")
```

## Data Source

The data for this visualization comes from the 
[TidyTuesday Taylor Swift dataset](https://github.com/rfordatascience/tidytuesday/tree/main/data/2023/2023-10-17).

**Original data citation:**  
Thompson, W. Jake. *taylor: Lyrics and Song Data for Taylor Swift's Discography*. 
Data sourced from Genius and the Spotify API.